Generating Simulated Data

### 2021-05-21 docs/SimData.Rmd
partial mapping agecl to lengthbin for diet

  survey_totN <- survey_N %>%
    group_by(species, agecl, time) %>%
    summarise(totN = sum(atoutput)) %>%
    ungroup()

  # sum over prey to get total consumption in t, divide by N and timestep, convert to g
  survey_totcons <- survey_cons %>%
    group_by(species, agecl, time) %>%
    summarise(totcons = sum(atoutput)) %>%
    ungroup() %>%
    left_join(survey_totN) %>%
    mutate(percap_cons = totcons/totN) %>%
    mutate(daily_percap_g = percap_cons/omlist_ss$runpar$outputstep*1000000)

@@

# divide by survey numbers at agecl to get per capita consumption at agecl

@@

We also plan to fit to time series of prey proportions for each predator size class. Gavin suggests an input format similar to those for survey lengths.

@@

>>>>

  # get rid of polygon
  survey_totN <- survey_N %>%
    group_by(species, agecl, time) %>%
    summarise(totN = sum(atoutput)) %>%
    ungroup()

  # sum over prey to get total consumption in t, divide by N and timestep, convert to g
  survey_totcons <- survey_cons %>%
    group_by(species, agecl, time) %>%
    summarise(totcons = sum(atoutput)) %>%
    ungroup() %>%
    left_join(survey_totN) %>%
    mutate(percap_cons = totcons/totN) %>%
    #mutate(daily_percap_g = percap_cons/omlist_ss$runpar$outputstep*1000000)
    mutate(daily_percap_g = percap_cons*1000000) #try assuming cons is snapshot not cumulative since last timestep

@@

@@

We also plan to fit to time series of prey proportions for each predator size class. Gavin suggests an input format similar to those for survey lengths. Diet output from surveys is by predator agecl

@@

# get size bins for predators
sizebins <- read_csv(paste0(o.name,"length_sizebins_NOBA.csv"))

# diet is by predator agecl, need diet by predator sizebin
# map predator agecl to lengthbin using length_comp_data from same survey

allsvdietprop <- tibble()

#multiple surveys named in list object, add to file
for(s in names(all_diets)){
  #arrange into long format: year, Species, agecl, length 
  svagelenbin <- len_comp_data[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, agecl, year, upper.bins, atoutput) %>%
    dplyr::left_join(modbins) %>%
    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, agecl, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::mutate(propage = sumlen/sum(sumlen)) #proportion of each agecl contributing to lengthbin

  svdietprop <- all_diets[[s]][[1]] %>%
    dplyr::mutate(year = ceiling(time.days/365)) %>%
    # join with agecl to length lookup
    dplyr::select(species, agecl, year, prey, dietSamp) %>%
    dplyr::left_join(svagelenbin) %>%

    dplyr::filter(modbin.min < upper.bins & upper.bins <= modbin.max) %>%
    dplyr::group_by(species, year, sizebin) %>%
    dplyr::summarise(sumlen = sum(atoutput)) %>%
    tidyr::spread(sizebin, sumlen) %>%
    ungroup() %>%
    dplyr::mutate(inpN = rowSums(.[,-(1:2)], na.rm = TRUE)) %>%
    dplyr::mutate(type = 0) %>%
    dplyr::mutate(survey = s) %>%
    dplyr::mutate_at(vars(contains("sizebin")), ~./inpN) %>%
    dplyr::select(survey, year, species, type, inpN, everything())
